Thermodynamic response functions in a cell fluid model

### 2024-09-13 paper_text.tex
figs for compilation in draft
add applicability part

Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ as a function of density $\rho^*$ (see Fig.~\ref{fig1}a), and the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
\begin{figure}[h!]
	%\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
	%\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
	\includegraphics[width=\column]{f1a1.pdf} 
	\includegraphics[width=\column]{f1b1.pdf}
	\vskip-3mm
	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines. Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
	}
	\label{fig1}
\end{figure}

@@

\begin{figure}[htbp]
	%\includegraphics[width=0.5\textwidth]{f2a.pdf}
	\includegraphics[width=\column]{f2a}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
	}
	\label{fig2a}
\end{figure}

\begin{figure}[h!] 
	%\includegraphics[width=0.45\textwidth]{f2b.pdf}
	%\includegraphics[width=0.475\textwidth]{f2c.pdf}
	\includegraphics[width=\column]{f2b.pdf}
	\includegraphics[width=\column]{f2c.pdf}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part~(a) covers a wider range of $M$. Part~(b) focuses on a range of $M$ around its critical value $0$.
	}
	\label{fig2b}
\end{figure}

@@

\begin{figure}[h!] 
	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
	\includegraphics[width=\column]{f3a.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}
	\label{fig3a}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
	\includegraphics[width=\column]{f3b.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig3b}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
	\includegraphics[width=\column]{f3c.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}
	\label{fig3c}
\end{figure}

@@

\begin{figure}[h!] 
	%\includegraphics[width=0.5\textwidth]{f4a.pdf}
	\includegraphics[width=\column]{f4a.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig4a}
\end{figure}

\begin{figure}[h!]
	%\includegraphics[width=0.45\textwidth]{f4b.pdf}
	%\includegraphics[width=0.475\textwidth]{f4c.pdf}
	\includegraphics[width=\column]{f4b.pdf}
	\includegraphics[width=\column]{f4c.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part (a) covers a wider range of $M$. Part (b) focuses on a range of $M$ around its critical value~$0$.
	}
	\label{fig4b}
\end{figure}

>>>>

Note that the theoretical approach used here has certain limits of applicability. The point is that the equations of state \eqref{eq:eosMT} and \eqref{eq:eosNT} of the cell fluid model are derived from calculating the grand partition function in the zero mode approximation of the $\rho^4$-model. At one stage of the calculation, we establish an explicit connection between the effective chemical potential $\bar M$ and the density $\rho^*$ by solving the cubic equation, which is derived from combining equations~\eqref{eq:density} and~\eqref{eq:ro_M} (see \cite{KozlovskiiDobush2020}, Section 5). This equation has three roots. Two solutions are nonphysical because they consequently reflect a decrease in chemical potential with increasing density. The third solution, namely \eqref{eq:ro_nT}, indicates the growth of the chemical potential with increasing density, but it is only valid for a limited range of densities $\rho^*_{min} \leqslant \rho^* \leqslant \rho^*_{max}$, where 
	\begin{eqnarray}
		\rho^*_{min} &=& \rho^*_c - \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}, \\
		\rho^*_{max} &=& \rho^*_c + \left( \frac{\left( g_3^2 - 2 g_2 g_4\right)^3}{9 g_4^4}\right)^{\frac{1}{2}}. \nonumber
	\end{eqnarray}
	The density's marginal values vary depending on the selected parameters $\alpha^*$ and $p$. Providing the set of coefficients \eqref{params}, one has $\rho^*_{min} = 0.009$ and $\rho^*_{max} = 1.946$.

Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ as a function of density $\rho^*$ (see Fig.~\ref{fig1}a), and the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
\begin{figure}[h!]
	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
	%\includegraphics[width=\column]{f1a1.pdf} 
	%\includegraphics[width=\column]{f1b1.pdf}
	\vskip-3mm
	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines. Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
	}
	\label{fig1}
\end{figure}

@@

\begin{figure}[htbp]
	\includegraphics[width=0.5\textwidth]{f2a.pdf}
	%\includegraphics[width=\column]{f2a}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
	}
	\label{fig2a}
\end{figure}

\begin{figure}[h!] 
	\includegraphics[width=0.45\textwidth]{f2b.pdf}
	\includegraphics[width=0.475\textwidth]{f2c.pdf}
	%\includegraphics[width=\column]{f2b.pdf}
	%\includegraphics[width=\column]{f2c.pdf}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part~(a) covers a wider range of $M$. Part~(b) focuses on a range of $M$ around its critical value $0$.
	}
	\label{fig2b}
\end{figure}

@@

\begin{figure}[h!] 
	\includegraphics[width=0.5\textwidth]{f3a.pdf}
	%\includegraphics[width=\column]{f3a.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}
	\label{fig3a}
\end{figure}
\begin{figure}[h!]
	\includegraphics[width=0.5\textwidth]{f3b.pdf}
	%\includegraphics[width=\column]{f3b.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig3b}
\end{figure}
\begin{figure}[h!]
	\includegraphics[width=0.5\textwidth]{f3c.pdf}
	%\includegraphics[width=\column]{f3c.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}
	\label{fig3c}
\end{figure}

@@

\begin{figure}[h!] 
	\includegraphics[width=0.5\textwidth]{f4a.pdf}
	%\includegraphics[width=\column]{f4a.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig4a}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=0.45\textwidth]{f4b.pdf}
	\includegraphics[width=0.475\textwidth]{f4c.pdf}
	%\includegraphics[width=\column]{f4b.pdf}
	%\includegraphics[width=\column]{f4c.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part (a) covers a wider range of $M$. Part (b) focuses on a range of $M$ around its critical value~$0$.
	}
	\label{fig4b}
\end{figure}
